The evolution of the transcriptome of mammalian placentas

### 2016-09-20 manuscript/manuscript.Rnw
switch to bar plot

\begin{figure}
<<core.placenta.transcriptome,fig.width=8,fig.height=12,out.height="0.8\\textheight",echo=FALSE>>=
cptl <-
    core.placenta.transcriptome.long[!grepl("(min|median|max|all)_expression|all_but_",
                                            Species),]
cptl <- cptl[,Species:=factor(gsub("^([^ ])[^ ]* +([^ ]*)","\\1. \\2",capfirst(Species)),
                              levels=gsub("^([^ ])[^ ]* +([^ ]*)","\\1. \\2",
                                          capfirst(names(species.names))))]
print(ggplot(cptl,
             aes(y=human_name,x=Species))
      + geom_raster(aes(fill=log10(FPKM)))
      + scale_x_discrete(expand=c(0,0))
      + scale_y_discrete(expand=c(0,0))
      + scale_fill_gradient(low = grad.def[["low"]],
                            high = grad.def[["high"]],
                            space = grad.def[["space"]],
                            na.value = grad.def[["na.value"]],
                            limits=c(0,4),
                            guide=guide_colorbar(title=expression(log[10](FPKM)))
                            )
      + ylab("Human Ortholog Name")
      + xlab("Species")
      + theme_grey()
      + theme(legend.position="top",
              axis.ticks = element_blank(),
              axis.text.y = element_text(face="italic"),
              axis.text.x = element_text(angle = 90, hjust = 1, vjust=0,face="italic"))
      )
@ 
\caption{Core Placenta Transcriptome.
  \Sexpr{core.placenta.transcriptome.long[,length(unique(human_name))]}
  1:1 \human ortholog genes expressed (\ac{FPKM}$ \ge 10$) in the
  placenta of all \Sexpr{star.logs[,length(unique(species))]} species
  studied with housekeeping genes
  \cite{Eisenberg.ea2013:Humanhousekeepinggenesrevisited} removed
  ordered (from top to bottom) by median expression. Supplemental
  \cref{fig:core_placenta_transcriptome_shape} shows the shape of the
  distribution of the number of genes in the core placenta
  transcriptome if different FPKM and species restriction criteria are
  utilized.}
\label{fig:core_placenta_transcriptome}
\end{figure}

>>>>

\begin{figure}
<<core.placenta.transcriptome,fig.width=8,fig.height=12,out.height="0.8\\textheight",echo=FALSE>>=
cptl <-
    core.placenta.transcriptome.long[!grepl("(min|median|max|all)_expression|all_but_",
                                            Species),]
cptl <- cptl[,Species:=factor(gsub("^([^ ])[^ ]* +([^ ]*)","\\1. \\2",capfirst(Species)),
                              levels=gsub("^([^ ])[^ ]* +([^ ]*)","\\1. \\2",
                                          capfirst(names(species.names))))]

print(ggplot(cptl,aes(x=human_name,y=FPKM))+
      geom_boxplot(outlier.shape=NA)+
      scale_y_log10()+
      geom_point(aes(color=Species,shape=Species))+
      scale_shape_manual(guide=guide_legend(nrow=2,
                                            keywidth=unit(3,"mm"),
                                            keyheight=unit(3,"mm"),
                                            label.theme=element_text(face="italic",
                                                                     angle=0,
                                                                     size=9)),
                         values=0:18)+
      coord_flip()+
      theme(legend.position="bottom"))

# print(ggplot(cptl,
#              aes(y=human_name,x=Species))
#       + geom_raster(aes(fill=log10(FPKM)))
#       + scale_x_discrete(expand=c(0,0))
#       + scale_y_discrete(expand=c(0,0))
#       + scale_fill_gradient(low = grad.def[["low"]],
#                             high = grad.def[["high"]],
#                             space = grad.def[["space"]],
#                             na.value = grad.def[["na.value"]],
#                             limits=c(0,4),
#                             guide=guide_colorbar(title=expression(log[10](FPKM)))
#                             )
#       + ylab("Human Ortholog Name")
#       + xlab("Species")
#       + theme_grey()
#       + theme(legend.position="top",
#               axis.ticks = element_blank(),
#               axis.text.y = element_text(face="italic"),
#               axis.text.x = element_text(angle = 90, hjust = 1, vjust=0,face="italic")) 
#      )
@ 
\caption{Core Placenta Transcriptome.
  \Sexpr{core.placenta.transcriptome.long[,length(unique(human_name))]}
  1:1 \human ortholog genes expressed (\ac{FPKM}$ \ge 10$) in the
  placenta of all \Sexpr{star.logs[,length(unique(species))]} species
  studied with housekeeping genes
  \cite{Eisenberg.ea2013:Humanhousekeepinggenesrevisited} removed
  ordered (from top to bottom) by median expression. Supplemental
  \cref{fig:core_placenta_transcriptome_shape} shows the shape of the
  distribution of the number of genes in the core placenta
  transcriptome if different FPKM and species restriction criteria are
  utilized.}
\label{fig:core_placenta_transcriptome}
\end{figure}
